```{r, message=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(kableExtra)
library(tidyverse)
library(here)
library(class)
```

# Introduction
The analysis of Indoor Positioning Systems is a burgeoning field that necessitates the capability to forecast the location of objects within a building. With the continual expansion of the Internet of Things, research on predicting the location in indoor positioning systems has gained increasing relevance. Statistical methods are employed to monitor individuals and items within diverse settings such as retail stores, healthcare facilities, and warehouses, utilizing indoor positioning systems to comprehend various behaviors and provide valuable insights to IPS data users. Traditional Global Positioning Systems lack reliability within buildings, but the proliferation of Wireless Fidelity allows the utilization of Wi-Fi signals to construct indoor positioning systems that deliver nearly real-time information about the whereabouts of people or objects. The data is initially presented to us in a raw format, requiring an understanding of how it was obtained and formatted. This enables us to structure the data appropriately for analysis using statistical analysis languages like R and Python, employing supervised machine learning and k-nearest neighbors to predict locations.

# Variable Description Table in 3. Data section

According to documents provided by the client, the data contains the following variables in Table 1:
```{r echo=FALSE, message=FALSE}
# Create a sample data frame
data <- data.frame(
  Variable = c("time", "posX", "posY", "orientation", "mac", "signal", "rawTime", "angle"),
  Description = c("Time of Observation", "X coordinate inside building", "Y coordinate inside building", "Angle of observation", "MAC address of device", "Signal strength", "Number of milliseconds after 1/1/1970", "45 degree cutoff of orientation"),
  Data_Type = c("Time/Date", "Discrete", "Discrete", "Continuous", "Continuous", "Continuous", "Continuous", "Discrete"))
# Create the table using kable and kable_classic
kbl(data, caption = "Variable Description and Types") %>%
kable_classic(full_width = FALSE, html_font = "Cambria", font_size = 6)
```